---
title: "The 'confintr' Package"
author: "Michael Mayer"
date: "`r Sys.Date()`"
bibliography: "biblio.bib"
link-citations: true
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{outForest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

## Introduction

The aim of this vignette is to introduce the R package `confintr` for calculating classic and bootstrap confidence intervals.

Confidence intervals for the following parameters are available:

- mean (Student, Wald, bootstrap),

- proportion (Wilson, Clopper-Pearson, Agresti-Coutts, bootstrap),

- median and other quantiles (distribution-free binomial and bootstrap),

- variance and standard deviation (chi-squared, bootstrap),

- IQR and MAD (bootstrap only),

- skewness and kurtosis (bootstrap only),

- R-squared and the non-centrality parameter of the F distribution (parametric),

- Cramér's V and the non-centrality parameter of the chi-squared distribution (parametric and bootstrap),

- Pearson-, Spearman-, Kendall correlation coefficients (normal for Pearson, bootstrap for any),

- Mean, quantile and median differences of two samples (for quantile/median only bootstrap).

Many of the classic confidence intervals are discussed in [@smithson2003]. Bootstrap confidence intervals are described in [@efron1993] and implemented by the `boot` package [@ripley2019].

The package supports both one- and two-sided intervals.

## Installation

From CRAN:
```
install.packages("confintr")
```

Latest version from github:
```
library(devtools)
install_github("mayer79/confintr")
```

## Examples

```{r}
library(confintr)

# Mean
ci_mean(1:100)
ci_mean(1:100, type = "bootstrap")

# 95% value at risk
ci_quantile(rexp(1000), q = 0.95)

# IQR
ci_IQR(rexp(100), R = 999)

# Correlation
ci_cor(iris[1:2], method = "spearman", type = "bootstrap", R = 999)

# Proportions
ci_proportion(10, n = 100, type = "Wilson")
ci_proportion(10, n = 100, type = "Clopper-Pearson")

# R-squared
fit <- lm(Sepal.Length ~ ., data = iris)
ci_rsquared(fit, probs = c(0.05, 1))

# Kurtosis
ci_kurtosis(1:100)

# Mean difference
ci_mean_diff(10:30, 1:15)
ci_mean_diff(10:30, 1:15, type = "bootstrap", R  = 999)

# Median difference
ci_median_diff(10:30, 1:15, R  = 999)
```

## References

