---
title: "Using confintr"
author: "Michael Mayer"
date: "`r Sys.Date()`"
bibliography: "biblio.bib"
link-citations: true
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using confintr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

## Introduction

The aim of this vignette is to introduce the R package `confintr` for calculating one- and two-sided classic and bootstrap confidence intervals.

Confidence intervals for the following parameters are available:

- mean (Student, Wald, bootstrap),

- proportion (Wilson, Clopper-Pearson, Agresti-Coutts, bootstrap),

- median and other quantiles (distribution-free binomial and bootstrap),

- variance and standard deviation (chi-squared, bootstrap),

- IQR and MAD (bootstrap only),

- skewness and kurtosis (bootstrap only),

- R-squared and the non-centrality parameter of the F distribution (parametric),

- Cramér's V and the non-centrality parameter of the chi-squared distribution (parametric and bootstrap),

- the odds ratio of a 2x2 table (exact),

- Pearson-, Spearman-, Kendall correlation coefficients (normal for Pearson, bootstrap for any),

- Mean, quantile and median differences of two samples (for quantile/median only bootstrap).

Many of the classic confidence intervals on this list are discussed in [@smithson2003]. 

We offer different types of bootstrap intervals:

1. Normal ("norm") bootstrap confidence interval: This is the Wald/Student confidence interval using as standard error the standard deviation of the bootstrap distribution plus a bootstrap bias correction. Simple, but only first-order accurate and not transformation respecting.

2. Percentile ("perc") bootstrap confidence interval: Uses quantiles of the bootstrap distribution as confidence limits. Simple, but only first order accurate. Transformation respecting.

3. Basic ("basic") or reverse bootstrap confidence interval: Flipped version of the percentile approach, dealing with bias but at the price of having very unnaturally tailed sampling distributions. Only first order accurate.

4. Bias-corrected and accelerated ("bca") confidence interval: Refined version of the percentile bootstrap which is second order accurate and transformation respecting. Needs more replications than observations. **Usually our default.**

5. Student-t ("stud") bootstrap confidence interval: Refined version of the normal bootstrap that replaces the Student quantile by a custom quantile obtained from bootstrapping the variance of the bootstrapped statistic. Second order accurate but not transformation respecting. Requires a formula for the variance of the estimator, which `confintr` provides for the mean, the mean difference, the variance (and standard deviation) as well as for the proportion. **Used as the default for the mean and the mean difference.**

For details on bootstrap confidence intervals, we refer to [@efron1993]. We provide them through the widely used `boot` package [@ripley2019]. 

## Installation

From CRAN:
```
install.packages("confintr")
```

Latest version from github:
```
library(devtools)
install_github("mayer79/confintr")
```

## Examples

```{r}
library(confintr)

set.seed(1)

# Mean
ci_mean(1:100)
ci_mean(1:100, type = "bootstrap")

# 95% value at risk
ci_quantile(rexp(1000), q = 0.95)

# IQR
ci_IQR(rexp(100), R = 999)

# Correlation
ci_cor(iris[1:2], method = "spearman", type = "bootstrap", R = 999)

# Proportions
ci_proportion(10, n = 100, type = "Wilson")
ci_proportion(10, n = 100, type = "Clopper-Pearson")

# R-squared
fit <- lm(Sepal.Length ~ ., data = iris)
ci_rsquared(fit, probs = c(0.05, 1))

# Kurtosis
ci_kurtosis(1:100)

# Mean difference
ci_mean_diff(10:30, 1:15)
ci_mean_diff(10:30, 1:15, type = "bootstrap", R  = 999)

# Median difference
ci_median_diff(10:30, 1:15, R  = 999)
```

## References

